---
title: "MyGitPresentation"
author: "Mark S Spoto"
date: "August 13, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% addTiles()
my_map
```

## Leaflet example
You can add markers to your map one at a time using the
`addMarkers()` function by specifying the longitue and 
latitude.  ([Here's](https://twitter.com/drop/status/19927537330040832)
a tip if you tend to mix them up.)  You can specify popup
text for when you click on the marker with `popup`

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% addTiles() %>% addMarkers(lat=39.2980803, lng=-76.5898801, popup="Jeff Leek's office")
my_map
```

## Lat Long Markers
```{r, echo=FALSE}
set.seed(12345)

hopkinsIcon <- makeIcon(
  iconUrl = "http://brand.jhu.edu/content/uploads/2014/06/university.shield.small_.blue_.png"  
)

hopkinsSites <- c(
  "<a href='http://www.jhsph.edu/'>East Baltimore Campus</a>",
  "<a href='https://apply.jhu.edu/visit/homewood/'>Homewood Campus</a>",
  "<a href='http://www.hopkinsmedicine.org/johns_hopkins_bayview/'>Bayview medical Center</a>",
  "<a href='http://www.peabody.jhu.edu/'>Peabody Institue</a>",
  "<a href='http://carey.jhu.edu/'>Carey Business School</a>"
)
  
df <- data.frame(lat = runif(20, min = 39.2, max = 39.3),
                 lng = runif(20, min = -76.6, max = -76.5))

df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon, popup = hopkinsSites)
```

## Make Map Clusters
```{r, echo=FALSE}
df <- data.frame(lat = runif(500, min = 39.25, max = 39.35),
                 lng = runif(500, min = -76.65, max = -76.55))

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```


